---
title: "Vignette"
author: "Jerome Guitton"
date: '2023-05-25'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(stocksmart)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(tidyr)
library(icesSD)
library(icesSAG)
library(FPSI)
library(sf)
library(knitr)
library(kableExtra)
library(rredlist)
#test



```

# ICES, NOAA database with specific R packages

## NOAA stocksmart packages

We use stocksmart package to access stock information they provide and we format them in our Common Ices format using limits format for references points and fishdata for time series. 
limits.noaa and fishdata.noaa functions provide NOAA data formated as ICES one
```{r NOAA_formated_data}
limits.noaa.dta<-limits.noaa()

#stockdef.noaa.dta<-stockdef.noaa()

g1<-limits.noaa.dta %>% filter(fishstock=='Gag - Southern Atlantic Coast') %>% 
  ggplot()+geom_point((aes(x=evaluationyear,y=fmsy)))+ggtitle("FMSY for GAG SA coast")
g2<-limits.noaa.dta %>% filter(fishstock=='Gag - Southern Atlantic Coast') %>% 
  ggplot()+geom_point((aes(x=evaluationyear,y=msybtrigger)))+ggtitle("MSYBtrigger for GAG SA coast")
ggarrange(g1,g2)


fishdata.noaa.dta<-fishdata.noaa()


fishdata.noaa.dta %>% group_by(fishstock) %>% summarize(evaluationyear=max(evaluationyear))->last.eval
g1<-fishdata %>% filter(fishstock=='Gag - Southern Atlantic Coast') %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=landings)))+ggtitle("Landing provided by last available assessment /GAG SA coast")
g2<-fishdata.noaa.dta %>% filter(fishstock=='Gag - Southern Atlantic Coast') %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=meanf)))+ggtitle("Fish mort provided by last available assessment /GAG SA coast")
g3<-fishdata.noaa.dta %>% filter(fishstock=='Gag - Southern Atlantic Coast') %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=recruitment)))+ggtitle("Recruitment provided by last available assessment /GAG SA coast")
g4<-fishdata.noaa.dta %>% filter(fishstock=='Gag - Southern Atlantic Coast') %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=ssb)))+ggtitle("SSB provided by last available assessment /GAG SA coast")

ggarrange(g1,g2,g3,g4)

fishdata.noaa.dta %>% group_by(fishstock,evaluationyear) %>% summarize(year=max(year))->last.ts.year

fishdata.noaa.dta %>% inner_join(last.ts.year) %>% inner_join(limits) %>% 
  mutate(f_fmsy=meanf/fmsy,b_bmsy=tbiomass/msybtrigger) ->system1
  
g1<- system1 %>% filter(fishstock=='Gag - Southern Atlantic Coast') %>% 
  ggplot()+geom_point(aes(x=evaluationyear,y=f_fmsy))
g2<-system1 %>% filter(fishstock=='Gag - Southern Atlantic Coast') %>% 
  ggplot()+geom_point(aes(x=evaluationyear,y=b_bmsy))

ggarrange(g1,g2)


#usethis::use_data(limits.noaa.dta)
#usethis::use_data(stockdef.noaa.dta)
#usethis::use_data(fishdata.noaa.dta)


```

## ICES R packages

We use icesSD and icesSAG to get similar values from ICES (limits.ices and fishdata.ices provide our common formated data)

```{r ICES_formated_data}

#fishdata.ices.dta<-fishdata.ices(update=TRUE)
#limits.ices.dta<-limits.ices(update=TRUE)
fishdata.ices.dta<-fishdata.ices()
limits.ices.dta<-limits.ices(update=TRUE)

#usethis::use_data(limits.ices.dta)
#usethis::use_data(fishdata.ices.dta)




g1<-limits.ices.dta %>% filter(fishstock=='ank.27.8c9a') %>% 
  ggplot()+geom_point((aes(x=evaluationyear,y=fmsy)))+ggtitle("FMSY for ank.27.8c9a")
g2<-limits.ices.dta %>% filter(fishstock=='ank.27.8c9a') %>% 
  ggplot()+geom_point((aes(x=evaluationyear,y=msybtrigger)))+ggtitle("ank.27.8c9a")
ggarrange(g1,g2)


fishdata.ices.dta %>% group_by(fishstock) %>% summarize(evaluationyear=max(evaluationyear))->last.eval
g1<-fishdata.ices.dta %>% filter(fishstock=='ank.27.8c9a') %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=landings)))+ggtitle("Landing provided by last available assessment")
g2<-fishdata.ices.dta %>% filter(fishstock=='ank.27.8c9a') %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=meanf)))+ggtitle("Fish mort provided by last available assessment ")
g3<-fishdata.ices.dta %>% filter(fishstock=='ank.27.8c9a') %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=recruitment)))+ggtitle("Recruitment provided by last available assessment ")
g4<-fishdata.ices.dta %>% filter(fishstock=='ank.27.8c9a') %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=ssb)))+ggtitle("SSB provided by last available assessment /GAG SA coast")

ggarrange(g1,g2,g3,g4)




```

## Other Informations

Command to update information, need 4 parameters to connect to the online DB 
```{r eval=FALSE}
#limits.other.dta<-limits.other(update=TRUE,user=USERPASS,password=PASS,server=Monserveur,db=mabase)
#fishdata.other.dta<-fishdata.other(update=TRUE,user=USERPASS,password=PASS,server=Monserveur,db=mabase)
#stockdef.other.dta<-stockdef.other(update=TRUE,user=USERPASS,password=PASS,server=Monserveur,db=mabase)
#usethis::use_data(stockdef.other.dta,overwrite=TRUE)  

limits.other.dta<-limits.other()
fishdata.other.dta<-fishdata.other()
stockdef.other.dta<-stockdef.other()

stockdef.other.dta %>% distinct(sub_division_fao,geom) %>% mutate(test=as.numeric(st_area(geom))) %>% 
  filter(test==0)->atrouver


```


```{r eval=FALSE}


stock.int<-'swo-io'

fishdata %>% group_by(fishstock) %>% summarize(evaluationyear=max(evaluationyear))->last.eval

  g1<-fishdata %>% filter(fishstock==stock.int) %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=landings)))+ggtitle("Landing provided by last available assessment")
g2<-fishdata %>% filter(fishstock==stock.int) %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=meanf)))+ggtitle("Fish mort provided by last available assessment /GAG SA coast")
g3<-fishdata %>% filter(fishstock==stock.int) %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=recruitment)))+ggtitle("Recruitment provided by last available assessment /GAG SA coast")
g4<-fishdata %>% filter(fishstock==stock.int) %>%
  inner_join(last.eval) %>% 
  ggplot()+geom_line((aes(x=year,y=ssb)))+ggtitle("SSB provided by last available assessment ")

ggarrange(g1,g2,g3,g4)

fishdata %>% group_by(fishstock,evaluationyear) %>% summarize(year=max(year))->last.ts.year

fishdata %>% inner_join(last.ts.year) %>% inner_join(limits) %>% 
  mutate(f_fmsy=meanf/fmsy,b_bmsy=tbiomass/msybtrigger) ->system2
  
g1<- system2 %>% filter(fishstock==stock.int) %>% 
  ggplot()+geom_point(aes(x=evaluationyear,y=f_fmsy))
g2<-system2 %>% filter(fishstock==stock.int) %>% 
  ggplot()+geom_point(aes(x=evaluationyear,y=b_bmsy))

ggarrange(g1,g2)

```


# Mixing all data

## System 2

There are some discrepancies between the report page 26 and foloowing. In page 27 the indicator is calculted with the mean of Fcurrent/Fmsy over the stocks assessment that occurs since 6 years? But in the case study, it seems that the calculation is made only using the last available assessment and it's an average of Fishing mortalities overs the lat 6 years of the time serie over Fmsy (similar to the calculation made for the balance capacity).

After meeting 5/06/2023 the rules is :
1- We use the last available assessment . 
2- We use Average of F overs at least 6 years / Fmsy

The second questioin is when the area is higher than stocks one, we catch several fishstock -> do we consider the worst value of all stocks in the same area (see previous report) ?

```{r}

pre.score.2<-system.2(sci_name='SOLEA SOLEA',area='27')
tout<-system.2()
#if I want to get all the system2 species, leave the values as NULL

ggplot(pre.score.2)+geom_sf(aes(fill=fishstock))

pre.score.2 %>% st_drop_geometry() %>% kbl() %>%
  kable_styling()



```
For Solea, we have to check why for one fishstock we hhave 9 assessment over 6 years (4 for 2019). Maybe we have to filter on type of outputs in teh ICES webservice (Type of publication / Published / Update or ...)


# System 1

## IUCN data 

Les données IUCN sont collectées à partir de 3 fichiers Marines Fishes collectés ici :https://www.iucnredlist.org/resources/spatial-data-download
Pour pouvoir avoir une taille raisonable j'ai simplifié les polygone :

Sous postgres 

create table geo.iucn_dta_simpl as  
select id_no,upper(sci_name) as scientific_name,yrcompiled,freshwater,category,st_simplify(geom,0.1) as geom from geo.iucn_dta 

So i merge the 3 shapefile, then i import the merged one to a postgis database and then i simplify the geometry. At the end i download the shape to R and save the iucn.dta. You can now find it using data(iucn.dta) command

```{r}

#iucn.dta<-st_read(stock,query="select * from geo.iucn_dta_simpl")
#usethis::use_data(iucn.dta)  


#Number of species / lines by catégory
data(iucn.dta)
head(iucn.dta)
iucn.dta %>% st_drop_geometry() %>% group_by(category) %>% summarize(total=n())

# a map for each category
ggplot(iucn.dta)+geom_sf()+facet_grid(~category)


```


### Données IUCN au travers de l'api

For IUCN data we can use web service available through rredlist package 
The system.1.iucn function is dedicate tto the this second method. To be decide if one is more suitable than the other

We store the token is a file (outside the github repository)

```{r}

stockdef<-stockdef.other()

limits<-rbind(limits.noaa(),limits.other(),limits.ices())

fishdata<-rbind(fishdata.noaa(),fishdata.other(),fishdata.ices())

data(iucn.dta)
data(sensitive.dta)
data(area.dta)
data(iucn_to_stock_area)

token<-readLines('/home/jerome/CSTEP_2023/FPSI/iucn.token')
system.1.iucnws(sci_name='LOPHIUS PISCATORIUS',area='57.',iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,token=token)


#With ass is global
system.1.iucnws(sci_name='GADUS MORHUA',area='27.5.A',iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,token=token)
#With ass is local

system.1.2(sci_name='ANOPLOPOMA FIMBRIA',area='18',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area)

system.1.2(sci_name='ANOPLOPOMA FIMBRIA',area='18',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,iucn.token=token)
system.1.2(sci_name='SOLEA SOLEA',area='18',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,iucn.token=token)
system.1.2(sci_name='SOLEA SOLEA',area='37',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,iucn.token=token)

system.1.2.dta<-system.1.2("SEPIA OFFICINALIS",area='21',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,iucn.token=token)

score.transcript(system.1.2(sci_name='SEPIA OFFICINALIS',area='21',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,iucn.token=token))

score.transcript(system.1.2(sci_name='BROSME BROSME',area='27.14.A',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,iucn.token=token))

score.transcript(system.1.2(sci_name='BROSME BROSME',area='27.1',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,iucn.token=token))

system.2(sci_name='BROSME BROSME',area='27.14.A',stockdef,limits,fishdata)

tmp<-system.1.2(sci_name='GADUS MORHUA',area='27.5.A',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,iucn.token=token)
score.transcript(system.1.2(sci_name='GADUS MORHUA',area='27',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,iucn.token=token))

tmp<-system.1.2(sci_name='ABLENNES HIANS',area='27',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area,iucn.token=token)

score.transcript(tmp)
is.null(tmp$score)
```




## Sensitive species

La liste des espèces sensible est là enfin 
```{r}
#curl::curl_download("https://data.dtu.dk/ndownloader/files/37373044",destfile='sensitive.csv')

#sensitive.dta<-read.csv2("sensitive.csv")
#Attention blank at the end of scientfic name
#library(stringr)
#sensitive.dta<-sensitive.dta %>% mutate(scientific_name=str_trim(toupper(Species)))

#usethis::use_data(sensitive.dta,overwrite=TRUE)  

data(sensitive.dta)

head(sensitive.dta)

sensitive.dta %>% mutate(Rindorf=trunc(as.numeric(Rindorf_precautionary_F)/10)*10) %>% 
  group_by(Rindorf) %>% summarise(n=n()) %>% 
  ggplot()+geom_bar(aes(x=Rindorf,y=n),stat='identity')


```

## Mixing system 1 and 2

Now we have stock assessment information from limits and fishdata, iucn.dta and sensitive.dta. 

```{r}
#Number of stocks in system 2 database
dim(system2)

#Number of sensitive species
dim(sensitive.dta)

#Number of species/area for IUCN
dim(iucn.dta)


```
system2.iucn only take stock without system 1 and check if the species and area (spatial intersection) could help us to access to system1..
We can check it on RAJA CLAVATA stocks. 
The link between stock and IUCN area are the intersction between the two polygons

```{r}


stockdef<-stockdef.other()

limits<-rbind(limits.noaa(),limits.other(),limits.ices())

fishdata<-rbind(fishdata.noaa(),fishdata.other(),fishdata.ices())

data(iucn.dta)
data(sensitive.dta)
data(area.dta)
data(iucn_to_stock_area)


system.2(sci_name='LOPHIUS PISCATORIUS',area='27.',stockdef,limits,fishdata)
system.1(sci_name='LOPHIUS PISCATORIUSlmlm',area='27.',iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area)

system.1.2.dta<-system.1.2(sci_name='THUNNUS ALALUNGA',area='51.',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area)
system.1.2.dta<-system.1.2(sci_name='MERLUCCIUS MERLUCCIUS',area='SA 17',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area)

system.1.2.dta<-system.1.2(sci_name='Toto',area='SA 17',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area)
class(system.1.2.dta)
score.transcript(system.1.2.dta %>% st_drop_geometry())

system.1.2.dta<-system.1.2(sci_name='ANOPLOPOMA FIMBRIA',area='18',stockdef,limits,fishdata,iucn.dta,sensitive.dta,area.dta,iucn_to_stock_area)


data<-score.transcript(system.1.2.dta )
if (data$method[1]=='No score for this Stock without data') {print(data$method)}




limits %>% filter(fishstock=='ank.27.78abd')
fishdata %>% filter(fishstock=='ank.27.78abd')
```

After Stock cithout system2 -> link with IUCN 56 other stock could rely to a iucn category and finaly, with sensitive, 163 stocks could rely to sensitive species
```{r}
iucn.dta %>% right_join (reste.system2 %>% st_drop_geometry()) %>% filter(is.na(category))->system2.iucn.tmp.reste

system2.iucn.tmp.reste %>% left_join(sensitive.dta) %>% filter(!is.na(Rindorf_precautionary_F))->road.6

system2.iucn.tmp.reste %>% left_join(sensitive.dta) %>% filter(is.na(Rindorf_precautionary_F))->system2.iucn.sensitive.reste

```


The end here ?


```{r}
nstocks<-length(system2$fishstock)

nstocks_iucn<-length((system2 %>% st_drop_geometry( )%>% inner_join(iucn.dta))$fishstock)
print(paste("Joining stock from system2 to iucn species we decrease the number of stocks from ",nstocks," to ",nstocks_iucn,sep=''))

#L'ensemble des espèces avec présence dans les stocks et absence dans iucn
system2 %>% st_drop_geometry( )%>% left_join(iucn.dta) %>% dplyr::select(fishstock,scientific_name,category) %>% filter(is.na(category))

# That means by example that Acadian redfish - Gulf of Maine / Georges Bank	SEBASTES FASCIATUS is available in Stock Ass database but not in IUCN one

nstocks_sensitive<-length((system2 %>% inner_join(sensitive.dta))$fishstock) 
print(paste("Joining stock from system2 to sensitive species we decrease the number of stocks from ",nstocks," to ",nstocks_sensitive,sep=''))

#Pour l'exemple
system2 %>% st_drop_geometry()%>% left_join(sensitive.dta) %>% dplyr::select(fishstock,scientific_name,Species) %>% filter(is.na(Species))

# That means by exemple that Acadian redfish - Gulf of Maine / Georges Bank	SEBASTES FASCIATUS is available in Stock Ass database but not in sensitive one

#The same between sensitive an iucn
sensitive.dta %>% left_join(iucn.dta) %>% dplyr::select(Species,scientific_name,category) %>% filter(is.na(category))->reste.system2.et.1
# That means by exemple that ZEUS FABER is a sensitive specie but not included in IUCN list

reste.system2.et.1 %>% kbl() %>%
  kable_styling()

iucn.dta %>% st_drop_geometry() %>% arrange(scientific_name)->test


```

